Designing a \carbon{} Network for a Carbon-Neutral European Economy

### 2023-09-19 report/sections/abstract.tex
init work for journal paper

The transformation of the global energy system to reach climate-neutrality requires large investments into new technologies. \dots

>>>>

Achieving a carbon-neutral European economy requires internationally coordinated efforts across all energy sectors, especially those with hard-to-abate emissions like heavy industry. Against this backdrop, It is critical to assess the need for comprehensive carbon management involving technologies such as carbon capture, transport, use, and storage to develop an effective carbon strategy for climate neutrality.

This paper provides the first cost-optimal design for a European energy system that fully incorporates carbon management technologies including a carbon transport network, and considers all emissions-intensive sectors. It optimizes carbon technologies, hydrogen transport and storage, and the design of renewable energy sources.

We show that carbon management technologies aiming at net-zero emissions provide systemic flexibility to the European energy system. A carbon network is cost-effective at different carbon capture rates (200 - 1000 Mt/a), leading to average cost savings of €13 billion per year. The \carbon{} network enables viable point source carbon capture, reducing the need for direct air capture facilities. We show that high sequestration rates are cost-beneficial by allowing continued fossil fuel use in some sectors, but require massive capacity expansion which could jeopardize timely attainment of climate neutrality.

### 2023-09-19 report/sections/methods.tex
init work for journal paper

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{sequestration_map.pdf}
    \caption{Sequestration map}
    \label{fig:sequestration_map}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[width=\linewidth]{capacity_map_electricity_co2network_1000.pdf}
    \caption{Optimal capacities per of the electricity sector for a sequestration of 1000 Mt/a.}
    \label{fig:capacity_map_noco2network_1000}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[width=\linewidth]{capacity_map_carbon_co2network_1000.pdf}
    \caption{Optimal capacities per of the carbon sector for a sequestration of 1000 Mt/a.}
    \label{fig:capacity_map_noco2network_1000}
\end{figure}

\begin{figure*}
    \centering
    \includegraphics[width=\linewidth]{operation_map_carbon_co2network_1000.pdf}
    \caption{Optimal operation per sector for a sequestration of 1000 Mt/a.}
    \label{fig:operation_map_noco2network_1000}
\end{figure*}

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{operation_area_carbon_co2network.pdf}
    \caption{Balance of captured CO$_2$ emissions for the optimal operation with CO$_2$ network.}
    \label{fig:operation_area_carbon_co2network}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{operation_area_carbon_noco2network.pdf}
    \caption{Balance of captured CO$_2$ emissions for the optimal operation without CO$_2$ network.}
    \label{fig:operation_area_carbon_noco2network}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{operation_bar_co2network_200.pdf}
\end{figure}

>>>>

% \begin{figure}
%     \centering
%     \includegraphics[width=\linewidth]{sequestration_map.pdf}
%     \caption{Sequestration map}
%     \label{fig:sequestration_map}
% \end{figure}

% \begin{figure}[h]
%     \centering
%     \includegraphics[width=\linewidth]{capacity_map_electricity_co2network_1000.pdf}
%     \caption{Optimal capacities per of the electricity sector for a sequestration of 1000 Mt/a.}
%     \label{fig:capacity_map_noco2network_1000}
% \end{figure}

% \begin{figure}[h]
%     \centering
%     \includegraphics[width=\linewidth]{capacity_map_carbon_co2network_1000.pdf}
%     \caption{Optimal capacities per of the carbon sector for a sequestration of 1000 Mt/a.}
%     \label{fig:capacity_map_noco2network_1000}
% \end{figure}

% \begin{figure*}
%     \centering
%     \includegraphics[width=\linewidth]{operation_map_carbon_co2network_1000.pdf}
%     \caption{Optimal operation per sector for a sequestration of 1000 Mt/a.}
%     \label{fig:operation_map_noco2network_1000}
% \end{figure*}

% \begin{figure}
%     \centering
%     \includegraphics[width=\linewidth]{operation_area_carbon_co2network.pdf}
%     \caption{Balance of captured CO$_2$ emissions for the optimal operation with CO$_2$ network.}
%     \label{fig:operation_area_carbon_co2network}
% \end{figure}

% \begin{figure}
%     \centering
%     \includegraphics[width=\linewidth]{operation_area_carbon_noco2network.pdf}
%     \caption{Balance of captured CO$_2$ emissions for the optimal operation without CO$_2$ network.}
%     \label{fig:operation_area_carbon_noco2network}
% \end{figure}

% \begin{figure}
%     \centering
%     \includegraphics[width=\linewidth]{operation_bar_co2network_200.pdf}
% \end{figure}

### 2023-09-19 report/submissions/journal/paper/paper.tex
init work for journal paper

\documentclass[conference]{IEEEtran}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{cuted}  % Add the cuted package
\usepackage{caption}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{tabularx, multirow}
\usepackage{fancyhdr,lipsum}

% \IEEEoverridecommandlockouts
% % The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
% \fancypagestyle{firstpage}{% Page style for first page
%   \fancyhf{}% Clear header/footer
%   \fancyfoot[l]{}% Footer
% }
% \thispagestyle{firstpage}

% \usepackage{cleveref}

% \crefname{align}{}{}
% \Crefname{align}{Equation}{Equations}

\IEEEoverridecommandlockouts
\IEEEpubid{\makebox[\columnwidth]{979-8-3503-1258-4/23/\$31.00 ©2023 IEEE \hfill} \hspace{\columnsep}\makebox[\columnwidth]{ }}

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\usepackage[%
backend=biber,bibencoding=utf8, %instead of bibtex
language=auto,
style=ieee,
sorting=none, % nyt for name, year, title
maxbibnames=10, % default: 3, et al.
%backref=true,%
natbib=true % natbib compatibility mode (\citep and~\citet still work)
]{biblatex}
\bibliography{../../references.bib}
% Template from https://de.overleaf.com/latex/templates/ieee-conference-template/grfzhhncsfqn

@@

% \thanks{Fabian Hofmann is funded by the Breakthrough Energy Project "Hydrogen Integration and Carbon Management in Energy System Models".}

\author{
    \IEEEauthorblockN{Fabian Hofmann, Christoph Tries, Fabian Neumann, Lisa Zeyen, Tom Brown}
    \IEEEauthorblockA{\textit{Institute of Energy Technology} \\
        \textit{Technical University of Berlin}\\
        Berlin, Germany \\
        m.hofmann@tu-berlin.de}
    % \IEEEauthorblockN{Anonym Author}

}

@@

\begin{IEEEkeywords}
    carbon management, energy system modelling, CCU, CCS, sector-coupling
\end{IEEEkeywords}

>>>>

\documentclass[twocolumn]{article}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{cuted}  % Add the cuted package
\usepackage{caption}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{tabularx, multirow}
\usepackage{fancyhdr,lipsum}

\usepackage[%
backend=biber,bibencoding=utf8, %instead of bibtex
language=auto,
style=ieee,
sorting=none, % nyt for name, year, title
maxbibnames=10, % default: 3, et al.
%backref=true,%
natbib=true % natbib compatibility mode (\citep and~\citet still work)
]{biblatex}
\bibliography{../../references.bib}

@@

\author{
    Fabian Hofmann, Christoph Tries, Fabian Neumann, Lisa Zeyen, Tom Brown \\
    \textit{Institute of Energy Technology} \\
    \textit{Technical University of Berlin}\\
    Berlin, Germany \\
    m.hofmann@tu-berlin.de
}

@@
